Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-26 doc/bcspaper/article.tex
Fixed Maria's comments

Since the advent of the `Digital Age', the amount of information available to
researchers has been increasing drastically and relevant material is becoming
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. There are already a large number of
information retrieval and recommendation systems for scientific publications.
Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain.

@@

\subsection*{Collection of scientific articles} Partridge allows users to
upload any paper which is free of copyright restrictions.  For the purpose of
this study we needed a large set of papers that we could label with CoreSC to
investigate how this information assists classification into paper type.  Open
Access (OA) journals provide free read access to their papers, but many do not
permit the user of articles for data mining purposes. The Public Library of
Science (PLoS) journals contain large volumes of OA literature under a
permissive license that allows data mining.  They also use the PubMed Central
markup schema, which is compatible with SAPIENTA, for papers published through
their journal. The PLoS journals advanced search offers approximately 50 types
of paper through which to restrict the search.  Many of these paper type
categories contain too few papers to be useful, others are too specific (e.g.
{\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not clear
how these paper types have been identified. We chose to look at a range of
types, some of which we expect to overlap or have an unclear distinction.
These are namely: Essay, Correspondence, Case Study, Perspective, Viewpoint,
Opinion, Review, Research.

>>>>

Since the advent of the `Digital Age', the amount of information available to
researchers has been increasing drastically, relevant material is becoming
progressively more difficult to find manually and the need for an automated
information retrieval tool more apparent. There are already a large number of
information retrieval and recommendation systems for scientific publications.
Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain.

@@

\subsection*{Collection of scientific articles} Partridge allows users to
upload any paper which is free of copyright restrictions.  For the purpose of
this study we needed a large set of papers that we could label with CoreSC to
investigate how this information assists classification into paper type.  Open
Access (OA) journals provide free read access to their papers, but many do not
permit the user of articles for data mining purposes. The Public Library of
Science (PLoS) journals contain large volumes of OA literature under a
permissive license that allows data mining.  They also use the PubMed Central
markup schema, which is compatible with SAPIENTA, for papers published through
their journal. The PLoS journals advanced search offers approximately 50 types
of paper through which to restrict the search.  Many of these paper type
categories contain too few papers to be useful, others are too ad hoc (e.g.
{\it Message from PLoS}). Indeed it is not clear how these paper types have
been identified. We chose to look at a range of types, some of which we expect
to overlap or have an unclear distinction.  These are namely: Essay,
Correspondence, Case Study, Perspective, Viewpoint, Opinion, Review, Research.
